AIR4Children: Artificial Intelligence and Robotics for Children

### 2021-02-20 article/tex/main.tex
refactors tex and makefile to ci and local build; adds gitignore
ammends workflow; adds reference-simple and amends main.tex
ammeds main.tex with no modifications; moves references; ammends Makefile
submitted version

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
In this work, we proposed AIR4Children, artificial intelligence for children, as a way to (a) tackle aspects for inclusion, accessibility, transparency, equity, fairness and participation and (b) to create affordable child-centred materials in AI and robotics.
We present current challenges and opportunities for a child-centred approaches for AI and robotics (AIR). 
Similarly, we touch on open-sourced software and hardware technologies to make a more inclusive, transparent and fair participation of children in areas of AIR. 
Then, we describe the avenues that AIR4Children can take with the development of open-sourced software and hardware.
Similarly, we propose to follow the philosophy of Montessori education 
to help children to not only develop matematical thinking but also to internalise new concepts and learning skills through activities of movement and repetition with open source robots.
Finally, we add conclusions and mainly we pose the future work to go of AIR4children to putting in practice what is proposed here and measure the impact on AI and robotics of children. 
\end{abstract}

@@

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{../references/references}

>>>>

%\usepackage[%
%    style=ieee,
%    dashed=false,
%    doi=false,
%    isbn=false,
%    giveninits=true,
%    maxnames=10,
%]{biblatex}
%\usepackage{biblatex}
%\addbibresource{../references/references-simple.bib}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
In this work, we proposed AIR4Children, artificial intelligence for children, as a way to (a) tackle aspects for inclusion, accessibility, transparency, equity, fairness and participation and (b) to create affordable child-centred materials in AI and robotics.
We present current challenges and opportunities for a child-centred approaches for AI and robotics (AIR). 
Similarly, we touch on open-sourced software and hardware technologies to make a more inclusive, transparent and fair participation of children in areas of AIR. 
Then, we describe the avenues that AIR4Children can take with the development of open-sourced software and hardware.
Similarly, we propose to follow the philosophy of Montessori education 
to help children to not only develop mathematical thinking but also to internalise new concepts and learning skills through activities of movement and repetition with open source robots.
Finally, we add conclusions and mainly we pose the future work to go of AIR4children to putting in practice what is proposed here and measure the impact on AI and robotics of children. 
\end{abstract}

@@

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{../references/references-simple}
%\printbibliography
